%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer II} % Job title
    {F5 Networks} % Organization
    {Seattle, WA} % Location
    {2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Debugging and Fixing customer facing issues in the BIG-IP's LTM and DNS modules.}
        \item {Designed and Implemented BIG-IP feature to better manage core files and prevent loss of information necessary to diagnose why the core occured.}
        \item {Performed threat model assessments on new F5 features to ensure secure design of new features.}
        \item {Backend development in Python to interact various apis to populate data for F5 Bug Tracker https://support.f5.com/csp/bug-tracker}
        \item {Development of Continuous Integration Pipeline in Python to perform Build, Test, and Integration for maintenance releases.}
        \item {Maintenance on Perl script to interact various apis and generate release notes for BIG-IP maintenance releases.}
        \item {Contributed to F5 ansible's bigip\_device\_dns and bigip\_hostname modules.}
        \item {Implemented scripts that utilize GDB's Python-API to automate running of necessary commands.}
        \item {Mentored Intern and Junior Engineers.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {F5 Networks} % Organization
    {Seattle, WA} % Location
    {2015 - 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Web Development using Python-Flask}
        \item {Researched security vulnerabilities and how they affect the BIG-IP platform.}
        \item {Developed various scripts that interface with Perforce, Bugzilla, and MSSQL in Perl.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {GoldSim Technology Group} % Organization
    {Issaquah, WA} % Location
    {2013 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Wrote automated black box tests for the GoldSim software in Test Complete}
        \item {Quality Assurance on xLPR V2 Model GUI}
        \item {Manual testing of compatibility between models created in GoldSim 10.5 with GoldSim 11}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
